---
title: "WriteUp Linear Model with prediction"
author: "Dominic Garibay"
date: "2023-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)
require(tigerstats)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```


## Model 1 SIMS~ARM
### Scattered Plot


```{r}
basicNN <- ggplot(data,aes(x=SIMS,y=ARM))

```

```{r}
basicNN + geom_point()+ ggtitle("SIMS vs ARM")

```


This scatter plot reflects a positive correlation since some of the dots are showing a behavior of going up diagonally.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The numerical results confirmed the positive corelation of the scatter plot of SIM vs ARM 


### Inferential Results Model 1 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create target 

```{r}
target <- data.frame(ARM= 88, GRIP=44)
```

### Perdict Target Point of Model 1 

```{r}
predict(model.1,target,interval=c("prediction"))
```

### Scatter Plot for Model 1 with linear fit 


```{r}
basicNN <- ggplot(data,aes(x=SIMS,y=ARM))

```

```{r}
basicNN + geom_point()+ ggtitle("SIMS vs ARM")+geom_smooth(method=lm)

```




