---
title: "WriteUp Linear Model with prediction"
author: "Dominic Garibay"
date: "2023-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)
require(tigerstats)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```


## Model 1 SIMS~ARM
### Scattered Plot


```{r}
basicNN <- ggplot(data,aes(x=SIMS,y=ARM))

```

```{r}
basicNN + geom_point()+ ggtitle("SIMS vs ARM")

```


This scatter plot reflects a positive correlation since some of the dots are showing a behavior of going up diagonally.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The numerical results confirmed the positive corelation of the scatter plot of SIM vs ARM 


### Inferential Results Model 1 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create target 

```{r}
target <- data.frame(ARM= 88, GRIP=44)
```

### Perdict Target Point of Model 1 

```{r}
predict(model.1,target,interval=c("prediction"))
```

### Scatter Plot for Model 1 with linear fit 


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```

```{r}
basicNN + geom_point()+ ggtitle("SIMS vs ARM")+geom_smooth(method=lm)

```

## Model 2 SIMS~GRIP
### Scattered Plot


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point()+ ggtitle("SIMS vs GRIP") 

```

This scatter plot tells us the grip strength that workers need. The plot tells us that most of the population needs to have GRIP strength between 80 and 130. 


### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

This correlation value is lower than the SIMS vs ARM correlation value with 0.6860073 which tells us that SIMS vs ARM has a better fit than SIMS vs GRIP. 


### Inferential Results Model 2 

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

### Perdict Target Point of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

### Scatter Plot for Model 1 with linear fit 


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point()+ ggtitle("SIMS vs GRIP")+geom_smooth(method=lm)

```

Looking at the scatter plot of SIMS vs ARM and SIM vs GRIP, we can tell that the data in model 1 plot is more scattered across the end of the best fit line, however on Model 2 scatter plot we have less data point towards the ends of the best fit line. 


## Model 3 SIMS~ARM+GRIP
### Scatter Plot 

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation valuue for model three came out to be higher than model one and two.  


### Inferential Results Model 3

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```



### Perdict target points for Model 3

```{r}
predict(model.3,target,interval=c("prediction"))

model.3=(-5.433871+0.037311*ARM+0.024471*GRIP)
```



model.3=(-5.433871+0.037311*ARM+0.024471*GRIP)

### Comparing Models Using anova. 
## Model 1 vs Model 3 

```{r}
anova(model.1,model.3)
```

The p value when comparing Model 1 vs model 3 is .000004994 which is very small. This tells us that model 3 is better than model 1 as we know that model one is already listed in model 3. 

## Model 2 vs Model 3 


```{r}
anova(model.2,model.3)
```

The p value for this comparison between model 2 and model 3 is .000000001495. This p value tells us that ARM vs GRIP is giving more data than ARM vs SIMS. Also this value tells us that Model 3 is much better than Model 2 and model 3 is already includes model 2 data. 

```{r}
anova(model.1,model.2)
```

